% 
% Licensed to the Apache Software Foundation (ASF) under one
% or more contributor license agreements.  See the NOTICE file
% distributed with this work for additional information
% regarding copyright ownership.  The ASF licenses this file
% to you under the Apache License, Version 2.0 (the
% "License"); you may not use this file except in compliance
% with the License.  You may obtain a copy of the License at
% 
%   http://www.apache.org/licenses/LICENSE-2.0
% 
% Unless required by applicable law or agreed to in writing,
% software distributed under the License is distributed on an
% "AS IS" BASIS, WITHOUT WARRANTIES OR CONDITIONS OF ANY
% KIND, either express or implied.  See the License for the
% specific language governing permissions and limitations
% under the License.
% 

      \section{Overview.} 
      A DUCC service is defined by the following two criteria:
      \begin{itemize}
          \item A service is one or more long-running processes that await requests
            and return something in response. 
          \item A service that is managed by DUCC is accompanied by a small program called a
            ``pinger'' that the DUCC Service Manager uses to gauge the availability and health of
            the service.  This pinger must always be be present. DUCC will supply a default
            pinger for UIMA-AS services if none is specified.
            
            Users may supply their own ``pingers'' by supplying a Java class that implements
            the pinger API.  This is referred to as a ``custom'' pinger in this document. 
            There are a number of service registration options which  allow
            specification and parameterization of customn pingers.

          \end{itemize}
      The pinger API enables the following functions for custom pingers:
      \begin{itemize}
      \item increase and decrease the number of service instances, 
      \item manage failure restart policies, 
      \item enable and disable service autostart, 
      \item notify the Service Manager of the date of last use of a service, 
      \item notify the Service Manager of the health and availability of a service, 
      \item returns a string for display in the DUCC Web server to show relevent service information
      \end{itemize}
      

      A service is usually a UIMA-AS service, but DUCC supports any arbitrary process as a service.

      The DUCC Service Manager implements several high-level functions:
      
      \begin{itemize}
          \item Ensure services are available for jobs before allowing the jobs to start.
          \item Enable fast-fail for jobs which reference services which are unavailable.
          \item Start a service when it is referenced by a job, and stop it when no longer needed.
          \item Optionally start a service when DUCC is booted.
          \item Insure services remain operational across failures.
          \item Report service failures.
          \item Run service pingers and respond to the pinger API as needed.
       \end{itemize}

       When work enters the system with a declared dependency on a service, one of the following
       actions is tken:
       \begin{itemize}
          \item If the service is not registered, the work request is automatically canceled.
          \item If the service is not running, the Service Manager attempts to start it; the job
           remains queued until the service is started and its pinger reports good health.
         \item If the service exists but cannot be started, the work remains queued and error
             status is shown in the web server.  Once the service is working again the
             work is allowed to proceed.
           \item If the service processes are running but the pinger reports failure contacting the service,
               the work remains queued with error status shown in the webserver.  Once the service
               pinger indicates the service is functional again the work is allowed to proceed.
       \end{itemize}
                
    \section{Service Types.}
    \label{sec:services.types}
      DUCC supports two types of services: UIMA-AS and CUSTOM:
      
      \begin{description}
          \item[UIMA-AS] This is a "normal" UIMA-AS service. DUCC fully supports all aspects of UIMA-AS
            services with minimal effort from developers.  A default pinger is supplied by DUCC
            for UIMA-AS services.  It is legal to define a custom pinger for a UIMA-AS service.
            
          \item[CUSTOM] This is any arbitrary service.  Developers must provide a custom pinger
            and declare the pinger in the service registration.            
      \end{description}

      DUCC also supports services that are not managed by DUCC.  These are known as {\em ping-only}
      services.  The registration for a ping-only service contains only keywords needed to 
      support a pinger.  Ping-only services must be defined as custom services; there is no
      default pinger provided for ping-only services.

      \section{Service Instance IDs}
      \label{sec:service.service.ids}
      DUCC 2.0.0 introduces support for constant service instance IDs.  As a service is being
      started, the SM assigns monotonically increasing IDs to each service instance, starting
      with ID 0, up the the maximum number of instances started.

      If an instance exits unexpectedly, the SM respawns it (unless a failure threshold has been
      exceeded).  The new instance is assigned the same instance ID as the instance it replaces.
      This insures that, for example, instance ``three'' is always started as instance ``three'',
      maintained constant over failures and SM restarts.

      The instance ID is communicated to the process through the environment with the key
      {\tt DUCC\_SERVICE\_INSTANCE}.  This key may also be used in service registrations if it
      is desired to pass the instance ID via parameters of some sort.  For example:
\begin{verbatim}
        service_jvm_args   -DSERVICE_ID=${DUCC_SERVICE_INSTANCE}
        process_executable_args -i ${DUCC_SERVICE_INSTANCE}
\end{verbatim}

      \section{Service References and Endpoints} 
      \label{sec:service.endpoints}
      Services are identified by an entity called a {\em service endpoint}.  Jobs and other
      services use the registered service endpoint to indicate dependencies on specific
      services.

      A service endpoint is of the form 
\begin{verbatim}
      <service-type>:<unique id>
\end{verbatim}
      
      The {\em service-type} must be either UIMA-AS or CUSTOM.
      
      The {\em unique id} is any string needed to ensure the service is
      uniquely named.  For UIMA-AS services, the unique-id must be the same as the
      service endpoint specified in service's DD XML descriptor.  The UIMA-AS
      service endpoint is always of the form:
\begin{verbatim}
      UIMA-AS:queue-name:broker-url
\end{verbatim}
      where {\em queue-name} is the name of the ActiveMQ queue used by the service, and {\em broker-url}
      is the ActiveMQ broker URL.  For example
\begin{verbatim}
      UIMA-AS:WikipediaSearchServices:tcp://broker1:61616
      UIMA-AS:GoogleSearchServices:http://broker2:61618
\end{verbatim}

      Jobs or other services may register dependencies on specific services by listing one or more
      service endpoints int their specifications. See the 
      \hyperref[sec:cli.ducc-submit]{\em job } and 
      \hyperref[sec:cli.ducc-services]{\em services } CLI descriptions for details.
                       
      A service is registered with DUCC using the \hyperref[sec:cli.ducc-services]{ducc\_services}
      API/CLI. Service registrations are persisted by DUCC and last over DUCC and cluster restarts.

      \section{Service Management Policies}
      \label{sec:service.management-policy}

      The Service Manager implements these policies for managing services:
      \begin{description}

         \item[Autostarted Services] An autostarted service is automatically started when the DUCC
           system is first booted.  If an instance should die, DUCC automatically restarts the
           instance and continually maintains the registered number of service instances.

           To handle fatal errors in {\em autostarted} services, The Service Manager maintains a time
           window in which only a specific number of instance failures may occur.  If the number of
           failures within that window of time is excessive DUCC will set a {\em disabled} flag and
           no longer restart instances.  Instance which do not fail are left running.  The {\em
             disabled} flag must be manually reset once the problem is resolved before new instances
           can be started.

           The default failure policy is implemented in the service pingers. Service
           owners may redefine the policy by supplying their own pingers for a service.
          
         \item[Reference-started Services] A reference-started service is a registered service that
           is started only when referenced by another job or service. If the service is already
           started, the dependent job/service is marked ``Services Available'' and can be scheduled.. If
           not, the service registry is checked and if a matching enabled service is found, it is 
           started by DUCC.  While the service is being started, jobs are held ``Waiting For Services''
           to ensure the service is viable. Once the service has completed initialization and the pinger 
           indicates it is viable, all work waiting on it are then marked ``Services Available'' and
           started.  
          
           To handle fatal errors in {\em reference-started} services, The Service Manager maintains
           a time window in which only a specific number of instance failures may occur.  If the
           number of failures within that window of time is excessive DUCC will set a {\em disabled}
           flag and no longer restart instances.  Instance which do not fail are left running. The
           {\em disabled} flag must be manually reset once the problem is resolved before new
           instances can be started.
           
           When the last job or service that references the on-demand service exits, a timer is
           established to keep the service alive for a while, in anticipation that it will be needed
           again soon.  When the keep-alive timer expires, and there are no more dependent jobs or
           services, the reference-started service is automatically stopped to free up its resources
           for other work.  The time the service is allowed to remain alive is known as its
           {\em linger} time and can be controlled with the {\em service\_linger} keyword in the
           service registration.

        \item[Manually started services] A service may be started via the CLI if it is not
          already running and in the absence of references by other work.  A service which is
          manually stared by the CLI can only be stopped manually by the CLI.

          As is the case for {\em autostarted} and {\em reference-started} services, failed 
          instances will be restarted unless the number of failures within the failure window
          is exceeded and the {\em disable} flag is set.  

        \item[Ping-Only Services] 
          \phantomsection\label{subsub:services.ping-only}
          Ping-only services consist of only
          a ping thread.  The service itself is not managed in any way by DUCC.  This is useful for
          managing dependencies on services that are not under DUCC control: the pinger is used
          to assess the viability of the external service and prevent dependent jobs from
          continuing if the service is unavailable.

          Only CUSTOM services may be defined as ping-only services in this version of DUCC.

      \end{description}

      A service may be {\em stopped}; that is, no instances are running.  This state can occur
      if the service has experienced too many errors within its failure window, in which case
      the service is {\em disabled}, or because the service is not {\em autostarted} or {\em referenced} by
      other work. 

      If a manual {\em stop} is issued the service will be automatically {\em disabled} to insure it
      cannot be restarted (by {\em reference} or at boot with {\em autostart}) without manual
      intervention.

      In all cases, if a service is {\em disabled}, it must be manually {\em enabled} using the CLI.

      It is possible, via the CLI, to dynamically switch any service from any management policy
      to any other policy, as shown in the following table.

      See the \hyperref[sec:cli.ducc-services]{\em Service CLI } reference for details on the various 
      commands described in this section.

      \begin{tabular}{| l | l | p{6cm} | p{6cm} |}
        \hline
        Current Mode & Desired Mode & Action & Notes \\
        \hline
        \hline
        Autostart    & Manual       & Use CLI to modify registration to {\em autstart false}. & Service does not stop until requested by CLI. Service will not start at DUCC boot.\\
        \hline
        Autostart    & Reference    & Use CLI to modify registration to {\em autostart false} and {\em observe references}. & Service stops  after last reference exits, plus {\em linger} time.\\
        \hline
        Autostart    & {\em Stopped} & Use CLI to stop the service. & The CLI stop will by necessity {\em disable} the service to insure it remains stopped. \\
        \hline
        Reference    & Autostart    & Use CLI to modify registration to {\em autostart true}. & Service continues to run after last reference exits.  Service always started at DUCC boot. \\
        \hline
        Reference    & Manual       & Use CLI to {\em ignore references}. & Service continues to run after last reference exits. \\
        \hline
        Reference    & {\em Stopped} & Use CLI to stop the service. & The CLI stop will by necessity {\em disable} the service to insure it remains stopped. \\
        \hline
        Manual       & Autostart    & Use CLI to modify registraiton to {\em autostart true}. & Service will be started on DUCC boots. \\
        \hline
        Manual       & Reference    & Use CLI to {\em observe references}. & Service will stop after last referencing job exits, plus {\em linger} time.. \\
        \hline
        Manual      & {\em Stopped} & Use CLI to stop the service. & The CLI stop will by necessity {\em disable} the service to insure it remains stopped. \\
        \hline
        {\em Stopped} & Autostart    & Use CLI to modify registration to {\em autostart true}. & Service will start immediately. It may be necessary to {\em enable} the service as well.\\
        \hline
        {\em Stopped} & Reference    & Submit a job or service that references the service. & It may be necessary to {\em enable} the service as well. 
                                       The service will stop after the last referencing work exits, plus {\em linger}.  \\
        \hline
        {\em Stopped} & Manual       & Use CLI to start the service. &  The CLI start will also {\em enable} the service if necessary. \\
        \hline
      \end{tabular}
      
      \section{Service Pingers}
      \label{sec:service.pingers}
      A service pinger is a small program that queries a service on behalf of the DUCC Service
      Manager.  A default pinger is provided for UIMA-AS services and provides the following
      functions:
      \begin{itemize}
        \item Determine if the service is responsive by issuing a UIMA-AS ``get-meta'' call 
          to the service.
        \item Determine the health of the service by issuing a JMX call to the UIMA-AS broker
          to collect queueing statistics.
        \item Manages the failure window of the service.
        \item Returns a string with basic ActiveMQ statistics about the service, or
          error information if the service is deemed unusable.
        \item Returns date of last use of the service (as determined by presence or
          absence of service producers attached to the service queue).
      \end{itemize}

      Users may supply their own pingers.  The following additional functions are available for
      pingers.  Note that a ``custom'' pinger MAY be supplied for UIMA-AS services, and
      MUST be supplied for CUSTOM services.  Custom pingers use the Service Manager's
      ``pinger'' API to perform the following tasks:
      \begin{itemize}
        \item Inform the Service Manager if the service is viable.
        \item Inform the Service Manager if the service is ``healthy''.  Service ``health''
          is a heuristic used in the DUCC Web server as an alert that a service 
          is responding but may
          not be performing well.
        \item Manage service failure policies. Default failure-window policy is
          provided to all pingers by the DUCC API handler (optional).
        \item Return a string describing current service status, for use by the
          web server.
        \item Instruct the service manager to increase the number of instances (optional).
        \item Instruct the service manager to decrease the number of instances (optional).
        \item Enable and disable the services autostart flag (optional).
        \item Enable logging of a service's health and state (optional).
        \item Return date of last-use to the Service Manager for display in the
          webserver (optional).
      \end{itemize}

      \subsection{The Pinger API}

      Pingers are passed static information about the service at pinger-initialization
      time, and subsequently, current state of the service is provided on each call (ping).

      Information provided at initialization follows.  Most of this is
      provided in fields in the {\em AServicePing} base class.  See the Javadoc for 
      specific field names and types.

      \subsubsection{Pinger Initialization Data}
      Data provided once, during pinger intialization, includes:
      \begin{description}
        \item[Arguments] This is the {\em service\_ping\_arguments} string from the
          service registration.
        \item[Endpint] This is the CUSTOM:string or UIMA-AS:string endpoint provided
          in the service registration.
        \item[Monitor Rate] This is the rate at which the pinger will be called by
          the SM, as provided in DUCC's configuration.
        \item[Service ID] This is the unique numeric service ID assigned to the service
          by DUCC.
        \item[Log Enabled] Whether the service log is enabled, as specified by the
          {\em service\_ping\_dolog} registration parameter.
        \item[Maximum Allowed Failures] This is the value of the {\em instance\_failures\_limit}
          parameter, provided by DUCC configuration and optionally overridden by the
          service registration.
        \item[Instance Failure Window] This is the value of the {\em instance\_failures\_window}
          prameter, provided by DUCC configuration and optionally overridden by the
          service registration.
        \item[Autostart Enabled] This indicates whether the service registration currently
          has the {\em autostart} flag enabled.
        \item[Last Use] This is the time of last known use of the service, persisted and
          maintained over SM restarts.  It is 0 if unknown or the service has never been
              used.
      \end{description}
        
      \subsubsection{Pinger Dynamic Data}

      Information provided in each call (ping) consists of:
      \begin{description}
        \item[All Instance Information] This is an array consisting of the unique integer
          IDS of all running proceses implementing the service.  This includes instances
          which may not be currently viable for some reason (still initializing, for example).

        \item[Active Instance Information] This is an array consisting of the unique integer
          IDS of all running proceses implementing the service.  This is a subset of 
          ``All Instance Information'' and includes only the service instances that are advanced
          to Running state.

        \item[Reference Information] This is an array consisting of the unique integer
          IDS of all DUCC work (Jobs, other Services, etc) currently referencing the
          service.  
          
        \item[Autostart Enabled] The current state of the service's autostart flag.
          
        \item[Run Failures] This is the total number of instance failures for the 
          service since the last start of the SM.
      \end{description}

      Only a Java API is supported.

      \subsection{Declaring a Pinger in A Service}

      The following registration options are used for declaring and configuring pingers.  Any of these
      may be dynamically modified with the service CLI's {\em$--$modify} option.  Dynamically changing
      these causes the current pinger to be terminated and restarted with the new configuration.  See
      \hyperref[sec:cli.ducc-services]{ducc\_services} for details of the options:
      \begin{itemize}
        \item service\_ping\_arguments
        \item service\_ping\_class
        \item service\_ping\_classpath
        \item service\_ping\_jvmargs
        \item service\_ping\_timeout
        \item service\_ping\_dolog
        \item instance\_failures\_window
        \item instance\_failures\_limit
      \end{itemize}

      
      \subsection{Implementing a Pinger}
      Pingers must implement the class {\tt org.apache.uima.ducc.cli.AServicePing}.  See the
      Javadoc for the details of this class.

      Below is a sample CUSTOM pinger for a hypothetical service that returns four integers in
      response to a ping.  It illustrates simple use of the three required methods, {\em init()},
      {\em stop()}, and {\em getStatistics()}.

      \begin{figure}[H]
\begin{verbatim}
import java.io.DataInputStream;
import java.io.InputStream;
import java.net.Socket;
import org.apache.uima.ducc.cli.AServicePing;
import org.apache.uima.ducc.cli.ServiceStatistics;

public class CustomPing
    extends AServicePing
{
    String host;
    String port;
    public void init(String args, String endpoint) throws Exception {
        // Parse the service endpoint, which is a String of the form 
        //    host:port
        String[] parts = endpoint.split(":");
        host = parts[1];
        port = parts[2];
    }

    public void stop()  {  }

    private long readLong(DataInputStream dis) throws Exception {
        return Long.reverseBytes(dis.readLong());
    }

    public ServiceStatistics getStatistics() {
        // Contact the service, interpret the results, and return a state
        // object for the service.
        ServiceStatistics stats = new ServiceStatistics(false, false,"<NA>");
        try {
            Socket sock = new Socket(host, Integer.parseInt(port));
            DataInputStream dis = new DataInputStream(sock.getInputStream());

            long stat1 = readLong(dis); long stat2 = readLong(dis); 
            long stat3 = readLong(dis); long stat4 = readLong(dis);

            stats.setAlive(true);  stats.setHealthy(true);
            stats.setInfo(  "S1[" + stat1 + "] S2[" + stat2 + 
                            "] S3[" + stat3 + "] S4[" + stat4 + "]" );
        } catch ( Throwable t) {
        	t.printStackTrace();
            stats.setInfo(t.getMessage());
        }
        return stats;        
    }
}
\end{verbatim}
        \caption{Sample UIMA-AS Service Pinger}
        \label{fig:service.custom.pinger}

      \end{figure}
      
      \subsection{Building And Testing Your Pinger}
      This section provides the information needed to use the pinger API and build a
      custom pinger. 

      \paragraph{1. Establish a compilation CLASSPATH} One DUCC jar is required in the CLASSPATH to build your pinger:
\begin{verbatim}
      DUCC_HOME/lib/uima-ducc-cli.jar
\end{verbatim}      
      This provides the definition for the {\em AServicePing} and {\em ServiceStatistics} classes.

      \paragraph{2. Create a registration}Next, create a service registration for the pinger.  While
      debugging, it is useful set the directive
\begin{verbatim}
     service_ping_dolog = true
\end{verbatim}
      This will log any output from  {\tt System.out.println()} to the declared log directory
      for the service.  If not specified in the reqistration, this directory is:
\begin{verbatim}
     $HOME/ducc/logs/<serviceid>/services
\end{verbatim}
      where {\tt$<$servicid$>$} is the DUCC-assigned ID of your service.

      Once the pinger is debugged you may want to turn logging off.
\begin{verbatim}
     service_ping_dolog = false
\end{verbatim}
      
      A sample service registration may look something like the following.  Note that you do not need
      to include any of the DUCC jars in the classpath for the pinger.  DUCC will add the jars it
      requires to interact with the pinger automatically.  (However you may need other jars to
      provide UIMA, UIMA-AS, ActiveMQ, Spring, or other services.)
\begin{verbatim}
     bash-3.2$ cat myping.svc

     description              = Ping-only service
     service_request_endpoint = CUSTOM:localhost:7175
     service_ping_class       = CustomPing
     service_ping_classpath   = /myhome/CustomPing.class
     service_ping_dolog       = true
     service_ping_timeout     = 500
     service_ping_aruments    = Arg1 Arg2
     service_ping_jvm_args   = -DXmx50M
\end{verbatim}
       
      \paragraph{3. Register and start the pinger} Start up your custom service so the pinger has something to contact, then start
      the pinger.  It may be easier to debug the pinger if you initially start the service outside of DUCC. Once
      the pinger is working it is straightforward to integrate it into the pinger's service registration by merging
      the registration for the pinger with the registration for the service.

      That's it!  Check the web server to make sure the service ``comes alive''.  Check your pinger's
      debugging log if it doesn't.  Once registered, you can dynamically modify and restart the pinger at any time without
      reregistering the service or restarting the service by use of the {\tt $--$modify} option of the
      ducc\_services CLI:
\begin{verbatim}
     ducc_services --modify <serviceid> --service_ping_dolog true
     ducc_services --modify <serviceid> --service_ping_class OtherCustsomPing
                                        --service_ping_classpath /myhome/OtherCustomPing.class

\end{verbatim}
     where $<$serviceid$>$ is the id returned when you registered the pinger.

     \paragraph{4. If all else fails ...}
     If your pinger does not work and you cannot determine the reason, be sure you enable {\em service\_ping\_dolog} and
     look in your log directory, as most problems with pingers are reflected there.  As a last resort, you can
     inspect the the Service Manager's log in
\begin{verbatim}
     $DUCC_HOME/logs/sm.log
\end{verbatim}
     
    \subsection{Globally Registered Pingers}
    \label{subsec:services.pingers}

    A pinger may be registered with DUCC so that it is available to all users of DUCC services.  To do 
    this, a registration file containing only pinger-specific parameters is created in DUCC's runtime
    directory.   Such a pinger may then be designated for a service by using its registered filename
    instead of its class in the {\em service\_ping\_class} field of a registration.  There is no API or
    CLI to register such a pinger; only a DUCC administrator may create a global ping registration.

    A globally-registered pinger may then be designated to run as a thread inside the SM or as a
    process spawned and managed by the SM. A pinger that runs in a thread in the SM is
    called an {\em internal} pinger, and one that runs in a process is called an {\em external}
    pinger.  An {\em internal} pinger generally has nearly unmeasurable impact on the system,
    whereas {\em external} pingers will occupy full JVMs with processes of 50-100MB or more.
    
    A service may override any of the options of a globally-registered {\em external} pinger,
    thus allowing significant reuse of existing code.  Only the {\em service\_ping\_arguments} 
    of an {\em internal} pinger may be overridden howver.

    The default UIMA-AS pinger is permanently registered as an {\em internal} pinger.

    Globally registered pingers use a special boolean property, not suppored by the
    {\em ducc\_services} API/CLI, ``internal'', to determine whether the pinger is
    to be run internally to SM or as an external process.

    More Details of registering global pingers is found in the 
    \hyperref[chap:sm]{\em Administration section} of this document.

\section{Sample Pinger}
    
    A sample custom UIMA-AS pinger is provided in the Examples directory shipped 
    with DUCC in
\begin{verbatim}
     DUCC_HOME/examples/src/org/apache/uima/ducc/ping
\end{verbatim}
    
    This pinger increases or decreases the number of service instances based
    on the queue statistics found by querying ActiveMQ.  The goal of this
    pinger is to maintain the ActiveMQ ``enqueued time'' to be no more than
    some multiple of the average service time for a single item.  The factor
    used is a parameter passed in with the argument string.

    \subsection{Using the Sample Pinger}
    The following arguments may be specified to use the sample pinger with any UIMA-AS service.  The
    {\em service\_ping\_arguemnts} are specific to this pinger.
\begin{verbatim}
    service_ping_class=org.apache.uima.ducc.ping.SamplePing
    service_ping_arguments=meta-timeout=15010,broker-jmx-port=1099,window=5,min=1,
                           max=20,max-growth=3,fast-shrink=true,goal=2.5
    service_ping_classpath = ${DUCC_HOME}/lib/uima-ducc/examples/*:
                             ${DUCC_HOME}/apache-uima/lib/*:
                             ${DUCC_HOME}/apache-uima/apache-activemq/lib/*:
                             ${DUCC_HOME}/lib//springframework/*
    service_ping_dolog=True
    service_ping_timeout=10000

    instance_failures_window = ${ducc.sm.instance.failure.window}
    instance_failures_limit  = ${ducc.sm.instance.failure.max}    
\end{verbatim}

    The pinger may optionally registered as a ``global'' pinger with the Service Manager by placing
    one or both of the ping registrations by copying the two files
\begin{verbatim}
    org.apache.uima.ducc.ping.SamplePing
    org.apache.uima.ducc.ping.SamplePing.external
\end{verbatim}
    from
\begin{verbatim}
    DUCC_HOME/examples/ping
\end{verbatim}
    to
\begin{verbatim}
    DUCC_HOME/resources/service_monitors
\end{verbatim}
    
    If these ping registrations are set up, the pinger may be run as either an
    internal thread in the SM by specifying {\em org.apache.uima.ducc.ping.SamplePing}
    in a service registration, or as an external process to the SM by
    specifying {\em org.apache.uima.ducc.ping.SamplePing.external}. 

    If run as an internal thread, the {\em service\_ping\_arguments} may be overridden
    by any referencing service.  If run as an external process, any of the
    pre-registered arguments may be overridden by reference services.

    The following arguments are specified in a single single comma-delimited
    string containing the following initializaton parameters:
    \begin{description}
      \item[meta-timeout] Defines how long to wait for {\em get\_meta} to return.
      \item[broker-jmx-port] Defines the JMX port of the service's broker.
      \item[window] Defines the shrinkage/growth window size, in minutes.
      \item[enable-log] Enable extra logging.
      \item[min] The minimum number of service instances to maintain.
      \item[max] The maximum number of service instances to allow.
      \item[max-growth] The maximum number of instances to grow in a
        single request.
      \item[fast-shrink] If set, allow services to shrink if the
        queue depth is 0, even if consumer are connected.  Otherwise
        we do not shrink if consumers are attached to the queue.
      \item[goal] The multiplier of the ActiveMQ Broker's {\em average enqeue}
        time to attemp to maintain by managing the number of instances.
    \end{description}

    
    \subsection{Understanding  Sample Pinger}

    The best way to understand this pinger is to examine the code itself in the
    Examples directory.  Here we provide a brief line-by-line synopsis of the code.

    \paragraph{void init(String args, String ep)}
    This required method examines the service arguments and endpoint and establishes a monitor
    to issue {\em get-meta} calls to the service and {\em JMS} calls to the 
    ActiveMq broker.  The argument string {\em args} is described above.  The
    endpoint {\em ep} is the service endpoint used to register the service.

    \paragraph{Lines 100-119}
    These lines parse the endpoint {\em ep} its components comprising the
    UIMA-AS queue name and the URL to the service broker.

    \paragraph{Lines 121-125}
    These lines disable most UIMA-AS logging as these messages can be quite
    numerous.  However, during debugging it may be desired to change the logging
    levels here.

    \paragraph{Lines 130-172}
    These lines parse the service argument string {\em args} into its constituent
    parts and places the values in variables.  They initialize the expansion
    and deletion window and normalize it to one slot per minute, regardless of
    the actual ping rate.

    The window normalization uses the DUCC-supplied value {\em monitor\_rate}
    to determine the number of slots in the windows.
   
    \paragraph{Lines 176-177}
    These lines initialze the DUCC-supplied {\em UimaAsServiceMonitor} that
    queries the UIMA-AS queues, and it resets the queue statistics via JMX so the
    monitor can make accurate measurements.

    \paragraph{Lines 181-187}
    These lines implement the required {\em stop} method which is invoked when
    the Service Manager needs to stop the pinger for any reason.  They stop the
    ActiveMQ queue monitor and emit a shutdown message.

    \paragraph{Lines 191-240}
    These lines define the required {\em getStatistics} method.  This 
    method collelcts ActiveMQ statistics, issue {\em get-meta} to the
    service to see if it is responding, sets the formatted information
    string into the ping reply, and invokes the code to calculate a
    potential redeployment of service instances.

    \paragraph{Lines 245-248}
    These lines override the optional {\em getLastUse} method which
    simply returns the time of last known use of the service.  The actual
    value is calcultated in the pinger-specific {\em calculateNewDeployment}
    method, described below.

    \paragraph{Lines 253-298}
    These lines define the pinger-specific {\em calculateNewDeployment}
    method.  This is invoked after {\em get-meta} is called and after the
    UIMA-AS queue has been queried in ActiveMQ.  This is the key method of
    this pinger.  It uses information passed in on the last ping from the
    Service Manager in conjunction with information in the ActiveMQ queue
    to determine if more, or fewer service instances are needed to meet the
    performance goals.  If fewer instances are needed, it selects specific
    instances to stop.  The method is 
    \hyperref[subsec:services.calculate-new]{\em described in detail} below.

    \paragraph{Lines 407-410}
    These lines override the optional {\em getAdditions} method.  The method
    returns the number of new service intances required to meet performance
    goals, as calculated in
    \hyperref[subsec:services.calculate-new]{\em calculateNewDeployment}.

    Regardless of what this method returns, the Service Manager may choose
    not to start new instances, based on its configured maximum,
    {\em ducc.sm.max.instances} as defined in {\em ducc.properties}.

    \paragraph{Lines 416-419}
    These lines override the optional {\em getDeletions} method.  This
    method returns the specific service instances to be stopped, if any.
    
    The DUCC-assigned unique IDs of all service instances are passed in to
    the pinger on each ping.  These instances are monotonically increasing
    over time so pingers may assume that lower numbers represent older
    instances.


    \paragraph{Lines 429-480}
    These lines define a class used as a call-back on the UIMA-AS
    {\em get-meta} requests to determine the host and PID of the
    service instance responding to the {\em get-meta}.   If the
    {\em get-meta} request should timeout, this information can be used to
    help identify ailing or overloaded service instances.
    
    \subsection{Calculating New Deployments in the Pinger}
    \label{subsec:services.calculate-new}

    his section details the use of ActiveMQ queue statistics
    in conjunction with the Service Monitor data to calculate the number
    of service instances to increase or decrease.

    It is important that this code be very careful about ``smoothing'' the
    performance statistics to keep growth and shrinkage stable.  Things
    to take into consideration include:
    \begin{enumerate}
      \item Immediately after a new service instance becomes available to
        serve, if there is demand for this service, the ActiveMQ statistics
        will fluctuate for a few minutes until traffic stabilizes.  Thus
        decisions based on these statistics must reflect history as well as
        current information.

      \item Immediately after a client begins to use a service, the statistics
        will also fluctuate, again requiring smoothing.

      \item The DUCC work dispatching model will not over-dispatch work to the
        job processes.  Thus actual demand on a service is a function of the
        number of actively deployed and initialized JPs.  If the number of
        JPs decreases due to preemption, demand on the service by that job
        will decrease proportionally.  Similarly, demand can increase as the
        job expands.  

        It is common for demand on a service to ramp up slowly as
        a job enters the system, and increase rapidly as a job completes its
        initialization phase and starts to double.  Thus, the ActiveMQ statistics
        can be quite erratic for a while, until the job stabilizes.

        This again requires some sort of smoothing of the data when making
        decisions about service growth and shrinkage.
    \end{enumerate}
    
    To handle this data smoothing, the SamplePing classes uses two time-based {\em windows}, one for
    growth, and one for shrinkage, to keep growth and shrinkage stable.  The window size is defined
    in the service ping argument {\em window}.
    Each window period, if more
    services are needed, a mark is made in the current slot of the {\em expansion window}; otherwise
    the current slot is cleared.  Similarly, each period, if fewer services are needed, a mark is
    made in the {\em shrinkage window}; otherwise, the current slot is cleared.

    After the marks are made, if the {\em expansion window} has all slots filled,
    a request for new processes is made; thus, a short period of increased does not
    destabilize the system with a request for services that may be of little use.  
    Additionally, when a request is made, the number of new processes requested is
    capped by the ping argument {\em max-growth} to insure that the service
    grows smoothly.  And finally, if the service is already at some configured maximum
    number of instances, defined by the {\em max} parameter, no additional instances
    are requested.

    Similarly, the {\em shrinkage window} is used to govern shrinkage.  All slots must be
    filled, indicating the service has been over-provisioned for a while, before a request
    is made to delete instances.  The number of instnaces is never reduced below the
    configured {\em min} value.  As well, this particular pinger never shrinks by more than
    a single instance at a time, on the reasoning that it is more costly to start a new
    service than to maintain one for too long.  Only if there is no long-term use of 
    the extra instances are they reduced (as
    determined by the window).

    Given this introduction, we describe the key method in detail.

    \paragraph{Lines 262-277}
    These lines extract four quantities from the ActiveMQ statistics:
    \begin{enumerate}
      \item Average enqueue time, {\em eT}
      \item Current queue depth, {\em Q}
      \item The current number of service consumers {\em cc}
      \item The current number of service producers {\em pc}
    \end{enumerate}

    The code then gets the DUCC IDs of all the currently started service
    instances, and the number of instances that are started but still in
    their ``initialization'' phase.  This is important because instances that
    are still initializing are not servicing the queue, but will soon start
    to do so.  The current ActiveMQ statistics reflect do NOT yet reflect
    this however, they reflect only the instances that are actually serving.

    Finally, if there are service producers, we note the time of day to
    return to the SM as the last known use of this service by some process.

    \paragraph{Lines 267}
    This line calculates the number of Java threads per service instance, needed to calclate the
    maxium capacity of the service in its current deployment.

    (Note that in each UIMA-AS service, UIMA-AS itself occupies one thread, used to
    manage the service, and this thread manifests itself as a consumer
    on the queue.)

    \paragraph{Line 301}
    This declares {\em new\_ni}, the number of additional instances, if any.
    At the end of this method, new\_ni will either be 0 or $>$0.

    \paragraph{Lines 303-312}
    If the current queue depth is 0 (Q $==$ 0), we know a number of things:
    \begin{enumerate}
      \item The service is not over-provisioned; there is no work queued and
        waiting for some service.  We therefor do not need to expand.
      \item If there are no consumers, i.e. no clients that need work done,
        we are potentially over-provisioned, so we fill in a slot in the
        expansion window.  
        
        If there {\em are} consumers, we may not want to
        shrink because it is possible that one of the service instances is
        busy; we cannot tell.  So we allow the {\em fast-shrink} 
        ping argument to govern whether or not connected consumers may
        prevent service shrinkage.
    \end{enumerate}

    There is nothing else that can be said about a service if its 
    current queue depth is 0.

    \paragraph{Lines 312-360}

    If the queue depth is non-zero we are able to calculate the total
    service capacity and the amount each instance contributes to the
    total capacity.  From this we can determine 
    \begin{enumerate}
      \item whether the service is performing at or near its goal, 
      \item if the service is performing worse than its goal, how many
        new instances are needed to meet the goal, and
      \item if the service is performing better than its goal, how many
        instances can be given up and still meet the goal.
   \end{enumerate}

   Details follow.

   \paragraph{Lines 314 and 315}
   The average time a single instance takes to serve a single request, {\em Ti}  is given
   by the simple formula 

\begin{verbatim}
    Ti = (eT / Q) * active
\end{verbatim}
 where

   \begin{description}
     \item[eT] is the average time an item stays in queue (from AMQ),
     \item[Q] is the current queue depth (from AMQ),
     \item[active] is the current number of service instances (from SM)
   \end{description}

   Therefore the time taken by a single thread {\em Ti} is given by 
\begin{verbatim}
   Tt = Ti * nthreads
\end{verbatim}

   \paragraph{Lines 319 and 320}
   We want {\em Tt} to become close to the current
\begin{verbatim}
   Tt * goal 
\end{verbatim}

    where {\em goal} is given by the ping arguments.  The 
   current ratio of actual service time to desired is then given by
\begin{verbatim}
   r = eT / g
\end{verbatim}

   Because we know that the DUCC job driver will never over-commit; that is,
   we know the current demand will remain constant unless the jobs using the
   service expand or contract (which are relatively rare events), we can state
   that the number of service instances required is directly proportional
   to {\em r}.  

   If  $r > 1$ we may need more instances to meet our {\em goal} and if
   $r < 1$ we may be over-provisioned.

   \paragraph{Lines 325-347}
   If  $r > 1$ we may be over-provisioned.  We calculate the number of required
   instances by multiplying the current instances by {\em r} and rounding down.
   We account for instances that we know are starting but not yet started,
   cap on max instances per service, and again on max growth per cycle.

   If we still require additions, we make a mark in the expansion window, 
   otherwise we clear the expansion window.

   \paragraph{Lines 349-360}
   If $r < 1$ we need to calculate shrinkage.  Because starting instances
   is expensive we conservatively use $r < .5$ instead and make a mark
   in the shrinkage window.  

   Otherwise we clear the mark in the shinkage window.

   \paragraph{Lines 367-396}
   Finally we sum across the shrinkage and expansion windows.  If either
   window is full, we schedule growth (line 375, set the variable {\em additions})
   or shrinkage (line 388, set {\em deletions}).

   Note that to schedule shrinkage, we must choose a specific instance.  In this
   case we choose the {\em newest} instance, i.e. the one with the largest
   DUCC ID, as it is most likely not to have initialized, or perhaps not to
   have ``warmed up'' (i.e. caches filled, etc.).  We could choose more than
   one but this pinger is conservative and only shrinks by one instance
   each time.

   \subsection{Summary of Sample Pinger}
   This pinger illustrates these functions over-and above the functions provided
   by the default UIMA-AS pinger:
   \begin{enumerate}
     \item Use of pinger-specific arguments
     \item Use of information provided by SM on each ping (service instances
       active, total service instances,
     \item Use of performance information acquired from ActiveMQ
     \item Requesting new service instances of the SM
     \item Requesting that instances be removed by SM,
     \item Setting of last-use of a service
   \end{enumerate}

   It illustrates one mechanism for smoothing growth and shrinkage of a service
   to prevent thrashing in your system.

   It illustrates one mechanism for determining the actual performance of
   a service by analyzing ActiveMQ queueing statistics.
     
   It illustrates the use of ``globally registered pingers.''
